Accessible Legislative Information: Automatic Summarisation of Zambian Legislative Documents

### 2024-09-23 paper-icict24-automatic_summarisation_of_zambian_legislative_documents.tex
Introduction Section
Added research objectives to the Introduction
section

@@

>>>>

The main objective of the study presented in this paper was to develop an automated summarisation system that utilises the potential of Natural Language Processing (NLP) to greatly enhance the accessibility and understanding of legislative documents in Zambia for the broader population. The specific objectives of the study were as follows:
\begin{itemize}
    \item To determine the challenges that people have in understanding legal documents
    \item To design and implement NLP models for summarising legislative documents
    \item To evaluate the effectiveness of the natural language processing model
\end{itemize}

@@

\begin{figure}%%%%%[htbp]
\fbox{%
\scalebox{0.65}{\includegraphics{figures/img-icict24-summary1_output.png}}
}%
\caption{Summmary 1: .}
\label{fig:results_and_discussion:summarisation_models:summary1}
\end{figure}

\begin{figure}%%%%%[htbp]
\fbox{%
\scalebox{0.325}{\includegraphics{figures/img-icict24-summary2_output.png}}
}%
\caption{Summmary 2: .}
\label{fig:results_and_discussion:summarisation_models:summary2}
\end{figure}
